---
title: "PPCA Using the Givens Representation"
output: html_notebook
---

```{r load}
library(tidyverse)
library(rstan)
library(plotly)

source("../../Givens.R")
source("../../GenerateSynthetic.R")
source("../../Plotting.R")
```

# 3D Data on a 1D Line

## Create Synthetic Data

```{r}
# set dimensions
n <- 3
p <- 1
d <- n*p-p*(p+1)/2

# create a flat plane matrix
W <- InverseGivensTransform(c(0.0, pi/2), n, p)

N <- 100
data_three_one <- GenerateHighDimData(n = n, p = p, W = W, LambdaVec = c(2), sd = 1.0, N = N)

x <- data_three_one$x
#save(x, file = "experiments/uncertaintyQuantification/unstableEstimate.Rdata")
```

## Get Posterior in Stan with Mirrored Givens Representation

```{r, message=FALSE}
x_matrix <- as.matrix(x)
Sigma_hat <- (1/N)*t(x_matrix) %*% x_matrix

dat <- list(n = n, p = p, N = N, SigmaHat = Sigma_hat)
fit <- stan(file = "../../Stan/new_khatri/ppca_patch.stan", data = dat, chains = 1, iter = 1e4)
```

## Get Posterior in Stan without Mirrored Givens Representation

```{r}
fit_no_mirror <- stan(file = "../../Stan/new_khatri/ppca_patch_no_mirror.stan", data = dat, chains = 1, iter = 1e4)
```

## Compare Posteriors

```{r}
extract(fit, pars = "theta")$theta[,1] %>% qplot
extract(fit, pars = "theta")$theta[,2] %>% qplot

extract(fit_no_mirror, pars = "theta")$theta[,2] %>% qplot
```


# 3D Data on a 2D Plane

## Create Simulated Data

```{r}
# set dimensions
n <- 3
p <- 2
d <- n*p-p*(p+1)/2

# create a flat plane matrix
W <- InverseGivensTransform(rep(0.0, d), n, p)

N <- 15
data_three_two <- GenerateHighDimData(n = n, p = p, W = W, LambdaVec = c(2,1), sd = 1.0, N = N)

#x <- ThreeTwo$x %>% tbl_df
#save(x, file = "experiments/uncertaintyQuantification/unstableEstimate.Rdata")
load(file = "simulated_data_three_two.Rdata")
```

## Plot Frequentist Point Estimate (Classical PCA)

```{r}
W_hat <- princomp(x)$loadings
lambda_hat <- princomp(x)$sdev

# use special function to translate surface to a format plotly can use
points_hat <- GetSurfacePoints(x$V1, x$V2, W_hat[,1:2])
points_true <- GetSurfacePoints(x$V1, x$V2, W)

# plot points and surface
plot_ly(x, x = ~V1, y = ~V2, z = ~V3) %>% add_markers() %>%
  add_surface(x = ~points_hat$x, y = ~points_hat$y, z = ~points_hat$z, opacity = 0.98, colorscale = list("black", "orange"))

# plot surfaces together
plot_ly(showscale = FALSE) %>%
  add_surface(x = ~points_hat$x, y = ~points_hat$y, z = ~points_hat$z, opacity = 0.98) %>%
  add_surface(x = ~points_true$x, y = ~points_true$y, z = ~points_true$z)
```

Because of small amount of data and low signal to noise ratio, maxmimum likelihood estimate is bad. Lambda values are `r princomp(x)$sdev` and would lead us to believe data is two dimensional, but we would pick the wrong subspace with maximum likelihood.

## Get Posterior in Stan with Givens Representation

```{r, message=FALSE}
x_matrix <- as.matrix(x)
Sigma_hat <- (1/N)*t(x_matrix) %*% x_matrix

dat <- list(n = n, p = 3, N = N, SigmaHat = Sigma_hat)
fit <- stan(file = "../../Stan/new_khatri/ppca_patch.stan", data = dat, chains = 1, iter = 1e4)
```

## Explore Posterior

```{r}
s <- rstan::extract(fit)
lambda_posterior <- tibble(Lambda1 = s$lambdaReversed[,3], Lambda2 = s$lambdaReversed[,2], Lambda3 = s$lambdaReversed[,1]) %>%
  gather(Parameter, Sample)

cbPalette <- c("grey45","black","darkorange")

lambda_posterior %>%
  ggplot() +
  geom_histogram(aes(x = Sample, group = Parameter, fill = Parameter), alpha = 0.4, position = "identity", binwidth = 0.05) +
  scale_fill_manual(values=cbPalette) +
  xlim(0,3) +
  geom_vline(xintercept = 1.52, color = "grey45", alpha = 1, size = 1.0) +
  geom_vline(xintercept = 1.27, color = "black", alpha = 1, size = 1.0) +
  geom_vline(xintercept = 0.77, color = "darkorange", alpha = 1, size = 1.0) +
  xlab("Singular Values") +
  ylab("Posterior Sample Counts") +
  theme(text = element_text(size=14))# +
  #facet_grid(Parameter ~.)
```

```{r}
angle_samples <- tibble(GT = s$theta[1:9999,3], EMHMC = byrne_angles$X3*pi/2) %>%
  gather(Method, theta)

cbPalette <- c("black","darkorange")

angle_samples %>%
  ggplot(aes(x = theta, group = Method, fill = Method)) +
  geom_histogram(alpha = 0.4, position = "identity", binwidth = 0.05) +
  scale_fill_manual(values=cbPalette) +
  xlab(expression(theta[2*3])) +
  ylab("Posterior Sample Counts") +
  theme(text = element_text(size=14))
```

## Compare to Posterior Using EMHMC

```{r}
fit_ppca_likelihood <- stan("../../Stan/new_khatri/ppca_likelihood.stan", data = dat, chains = 1, iter = 1)

unconstrain_pars(fit_ppca_likelihood, list(Y = W, lambdaReversed = c(2,1), sigmaSq = 1.0))
emhmc_onesample_eigennetwork(U0 = W, L0 = c(2,1), c0 = , lp_ppca, grad_lp_ppca, h = , nsteps = 20)
```


# Scaling and Benchmarking

