---
title: "CCA"
output: html_notebook
---

```{r}
coagTestsStnd %>% names
```

- Vitals
    + temp, hr, resprate, sbp
- BG
    + paco2, pao2, hco3, serumco2, bun, basedefexc
- CBC
    + wbc, hct, hgb, plts
- Cascade
    + factorii, factorv, factorvii, factorviii, factorix, factorx, pc, atiii, log_ddimer
- PT
    + pt, ptt

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(rstan)
options(mc.cores = parallel::detectCores())

d <- function(n, p) n*p - p*(p+1)/2
p_common <- 2
n_0 <- 4
p_0 <- 2
d_W_0 <- d(n_0, p_common)
d_B_0 <- d(n_0, p_0)

n_1 <- 6
p_1 <- 4
d_W_1 <- d(n_1, p_common)
d_B_1 <- d(n_1, p_1)

n_2 <- 4
p_2 <- 2
d_W_2 <- d(n_2, p_common)
d_B_2 <- d(n_2, p_2)

n_3 <- 9
p_3 <- 7
d_W_3 <- d(n_3, p_common)
d_B_3 <- d(n_3, p_3)

n_4 <- 2
p_4 <- 1
d_W_4 <- d(n_4, p_common)
d_B_4 <- d(n_4, p_4)

sigmaSqHyperPrior <- 1
ardHyperHyperPrior <- 10
sparseHyperHyperPrior <- 10

N <- nrow(coagTestsStnd)
X <- as.matrix(coagTestsStnd)
SigmaHat <- (1/N)*t(X) %*% X

data <- list(n_0 = n_0, p_0 = p_0, n_1 = n_1, p_1 = p_1, n_2 = n_2, p_2 = p_2, n_3 = n_3, n_4 = n_4, p_4 = p_4, p_common = p_common,
             d_W_0 = d_W_0, d_B_0 = d_B_0, d_W_1 = d_W_1, d_W_1 = d_W_1, 
             d_W_2 = d_W_2, d_B_2 = d_B_2, p_3 = p_3, d_W_3 = d_W_3, d_B_3 = d_B_3, 
             d_W_4 = d_W_4, d_B_4 = d_B_4,
             sigmaSqHyperPrior = sigmaSqHyperPrior, ardHyperHyperPrior = ardHyperHyperPrior,
             sparseHyperHyperPrior = sparseHyperHyperPrior, N = N, SigmaHat = SigmaHat)

#fit <- stan(file = "../../Stan/CcaGen.stan", data = data, chains = 8, iter = 10000)

m <- stan_model(file = "../../Stan/CcaGen.stan")
#system.time(vi <- vb(m, data = data))
```

# MAP Estimate

```{r}
system.time(op <- optimizing(m, data = data, iter = 10000))

summary(vi, pars = c("ardHyperPrior", "sparseHyperPrior"))$summary
op$par[c("ardHyperPrior", "sparseHyperPrior")]

map <- op$par
theta_W_0 <- map[1:5]
theta_W_1 <- (map[grepl("theta_W_1", names(map))])[1:d_W_1]
theta_W_2 <- (map[grepl("theta_W_2", names(map))])[1:d_W_2]
theta_W_3 <- (map[grepl("theta_W_3", names(map))])[1:d_W_3]
theta_W_4 <- (map[grepl("theta_W_4", names(map))])[1:d_W_4]

lambda_0_med <- c(map["lambda_0[1]"],map["lambda_0[2]"])
lambda_1_med <- c(map["lambda_1[1]"],map["lambda_1[2]"])
lambda_2_med <- c(map["lambda_2[1]"],map["lambda_2[2]"])
lambda_3_med <- c(map["lambda_3[1]"],map["lambda_3[2]"])
lambda_4_med <- c(map["lambda_4[1]"],map["lambda_4[2]"])

W_0 <- InverseGivensTransform(theta_W_0, n_0, p_common)
dimnames(W_0) <- list(names(coagTestsStnd)[1:4], c("Latent1", "Latent2"))
W_0 * lambda_0

W_1 <- InverseGivensTransform(theta_W_1, n_1, p_common)
dimnames(W_1) <- list(names(coagTestsStnd)[5:10], c("Latent1", "Latent2"))
W_1 * lambda_1

W_2 <- InverseGivensTransform(theta_W_2, n_2, p_common)
dimnames(W_2) <- list(names(coagTestsStnd)[11:14], c("Latent1", "Latent2"))
W_2 * lambda_2

W_3 <- InverseGivensTransform(theta_W_3, n_3, p_common)
dimnames(W_3) <- list(names(coagTestsStnd)[15:23], c("Latent1", "Latent2"))
W_3 * lambda_3

#InverseGivensTransform(theta_W_4_Gsw_med, n_4, p_common)

RightRotateCounterClockwise(diag(2), theta_W_4,1,2) * lambda_4
```

# Most Representative Sample

```{r}
s <- extract(vi)

getSamplesCloseToMed <- function(x) {
  lower <- quantile(x, probs = c(0.4,0.6))[1]
  upper <- quantile(x, probs = c(0.4,0.6))[2]
  
  return(which(x >= lower & x <= upper))
}

getSamplesCloseToMed(s$theta_W_0[,2]) %>%
  intersect(getSamplesCloseToMed(s$theta_W_1[,2])) %>%
  intersect(getSamplesCloseToMed(s$theta_W_2[,2])) %>%
  intersect(getSamplesCloseToMed(s$theta_W_3[,2]))

sampleId <- 204

theta_W_0 <- s$theta_W_0[sampleId,]
theta_W_1 <- s$theta_W_1[sampleId,]
theta_W_2 <- s$theta_W_2[sampleId,]
theta_W_3 <- s$theta_W_3[sampleId,]
theta_W_4 <- s$theta_W_4[sampleId,]

lambda_0 <- s$lambda_0[sampleId,]
lambda_1 <- s$lambda_1[sampleId,]
lambda_2 <- s$lambda_2[sampleId,]
lambda_3 <- s$lambda_3[sampleId,]
lambda_4 <- s$lambda_4[sampleId,]

W_0 <- InverseGivensTransform(theta_W_0, n_0, p_common)
dimnames(W_0) <- list(names(coagTestsStnd)[1:4], c("Latent1", "Latent2"))
W_0 * lambda_0

W_1 <- InverseGivensTransform(theta_W_1, n_1, p_common)
dimnames(W_1) <- list(names(coagTestsStnd)[5:10], c("Latent1", "Latent2"))
W_1 * lambda_1

W_2 <- InverseGivensTransform(theta_W_2, n_2, p_common)
dimnames(W_2) <- list(names(coagTestsStnd)[11:14], c("Latent1", "Latent2"))
W_2 * lambda_2

W_3 <- InverseGivensTransform(theta_W_3, n_3, p_common)
dimnames(W_3) <- list(names(coagTestsStnd)[15:23], c("Latent1", "Latent2"))
W_3 * lambda_3

#InverseGivensTransform(theta_W_4_Gsw_med, n_4, p_common)

RightRotateCounterClockwise(diag(2), theta_W_4,1,2) * lambda_4
```

# Posterior Marginal Medians

```{r}
posterior <- as.array(vi)
#mcmc_intervals(posterior, pars = c("lambda_0[1]", "lambda_0[2]"))

posteriorMedian <- summary(vi)$summary[,"50%"]
theta_W_0_Gsw_med <- posteriorMedian[1:5]
theta_W_1_Gsw_med <- (posteriorMedian[grepl("theta_W_1", names(posteriorMedian))])[1:d_W_1]
theta_W_2_Gsw_med <- (posteriorMedian[grepl("theta_W_2", names(posteriorMedian))])[1:d_W_2]
theta_W_3_Gsw_med <- (posteriorMedian[grepl("theta_W_3", names(posteriorMedian))])[1:d_W_3]
theta_W_4_Gsw_med <- (posteriorMedian[grepl("theta_W_4", names(posteriorMedian))])[1:d_W_4]

lambda_0_med <- c(posteriorMedian["lambda_0[1]"],posteriorMedian["lambda_0[2]"])
lambda_1_med <- c(posteriorMedian["lambda_1[1]"],posteriorMedian["lambda_1[2]"])
lambda_2_med <- c(posteriorMedian["lambda_2[1]"],posteriorMedian["lambda_2[2]"])
lambda_3_med <- c(posteriorMedian["lambda_3[1]"],posteriorMedian["lambda_3[2]"])
lambda_4_med <- c(posteriorMedian["lambda_4[1]"],posteriorMedian["lambda_4[2]"])

W_0_Gsw_med <- InverseGivensTransform(theta_W_0_Gsw, n_0, p_common)
dimnames(W_0_Gsw_med) <- list(names(coagTestsStnd)[1:4], c("Latent1", "Latent2"))
W_0_Gsw * lambda_0_med

W_1_Gsw_med <- InverseGivensTransform(theta_W_1_Gsw, n_1, p_common)
dimnames(W_1_Gsw_med) <- list(names(coagTestsStnd)[5:10], c("Latent1", "Latent2"))
W_1_Gsw * lambda_1_med

W_2_Gsw_med <- InverseGivensTransform(theta_W_2_Gsw, n_2, p_common)
dimnames(W_2_Gsw_med) <- list(names(coagTestsStnd)[11:14], c("Latent1", "Latent2"))
W_2_Gsw * lambda_2_med

W_3_Gsw_med <- InverseGivensTransform(theta_W_3_Gsw, n_3, p_common)
dimnames(W_3_Gsw_med) <- list(names(coagTestsStnd)[15:23], c("Latent1", "Latent2"))
W_3_Gsw_med * lambda_3_med

RightRotateCounterClockwise(diag(2), theta_W_4_Gsw_med,1,2) * lambda_4_med

dimnames(SigmaHat) <- list(names(coagTestsStnd), names(coagTestsStnd))
```


# Sub Cohorts

```{r}

quant <- function(x, prob) quantile(x, probs = c(prob), na.rm = TRUE)[1]

coagSummary <- CoagImputed1 %>%
  group_by(mechtype) %>%
  summarize(n = n(),
            pctMale = mean(male == "Male"),
            meanAge = mean(age), sdAge = sd(age),
            meanBmi = mean(bmi, na.rm = TRUE), sdBmi = sd(bmi, na.rm = TRUE),
            pctBlunt = mean(blunt == "Blunt"),
            pctTbi = mean(tbi == "Yes"),
            meanArrivalGcs = mean(edarrivalgcs, na.rm = TRUE), sdArrivalGcs = sd(edarrivalgcs, na.rm = TRUE),
            pctHadribfxs = mean(numribfxs > 0,na.rm = TRUE),
            pctIntubate = mean(admitday_intubated == "Yes"),
            pctHeadInj = mean(aishead1 > 0),
            pctFaceInj = mean(aisface2 > 0),
            pctChestInj = mean(aischest3 > 0),
            pctAbdomenInj = mean(aisabdomen4 > 0),
            pctExtremityInj = mean(aisextremity5 > 0),
            Q10bloodUnits = quant(icu_0to6h_blood_units, 0.1),
            Q50bloodUnits = quant(icu_0to6h_blood_units, 0.5), 
            Q900bloodUnits = quant(icu_0to6h_blood_units, 0.9)) %>%
  arrange(desc(n))
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
coagTestsStndMechtype <- coagTestsStnd %>% mutate(mechtype = CoagImputed1$mechtype)

ardHyperHyperPrior <- 0.2
sparseHyperHyperPrior <- 0.2
n <- n_0+n_1+n_2+n_3+n_4
J <- 7
N <- rep(0, J)


getSigmaHat <- function(df) {
  X <- as.matrix(df)
  N <- nrow(df)
  return((1/N)*t(X) %*% X)
}

SigmaHat <- array(0, dim = c(J, n, n))

#GSW
coagTestsStndGsw <- coagTestsStndMechtype %>% filter(mechtype == "GSW") %>% select(-mechtype)
SigmaHat[1,,] <- getSigmaHat(coagTestsStndGsw)
N[1] <- nrow(coagTestsStndGsw) 

#Fall
coagTestsStndFall <- coagTestsStndMechtype %>% filter(mechtype == "Fall/Crush") %>% select(-mechtype)
SigmaHat[2,,] <- getSigmaHat(coagTestsStndFall)
N[2] <- nrow(coagTestsStndGsw) 

#MVC
coagTestsStndMvc <- coagTestsStndMechtype %>% filter(mechtype == "MVC") %>% select(-mechtype)
SigmaHat[3,,] <- getSigmaHat(coagTestsStndMvc)
N[3] <- nrow(coagTestsStndMvc) 

#PVA
coagTestsStndPva <- coagTestsStndMechtype %>% filter(mechtype == "PVA") %>% select(-mechtype)
SigmaHat[4,,] <- getSigmaHat(coagTestsStndPva)
N[4] <- nrow(coagTestsStndPva) 

#SW
coagTestsStndSw <- coagTestsStndMechtype %>% filter(mechtype == "SW") %>% select(-mechtype)
SigmaHat[5,,] <- getSigmaHat(coagTestsStndSw)
N[5] <- nrow(coagTestsStndSw) 

#Assault
coagTestsStndAssault <- coagTestsStndMechtype %>% filter(mechtype == "Assault") %>% select(-mechtype)
SigmaHat[6,,] <- getSigmaHat(coagTestsStndAssault)
N[6] <- nrow(coagTestsStndAssault) 

#Bike
coagTestsStndBike  <- coagTestsStndMechtype %>% filter(mechtype == "BVA/Bike") %>% select(-mechtype)
SigmaHat[7,,] <- getSigmaHat(coagTestsStndBike)
N[7] <- nrow(coagTestsStndBike) 

data <- list(n_0 = n_0, p_0 = p_0, n_1 = n_1, p_1 = p_1, n_2 = n_2, p_2 = p_2, n_3 = n_3, n_4 = n_4, p_4 = p_4, p_common = p_common,
             d_W_0 = d_W_0, d_B_0 = d_B_0, d_W_1 = d_W_1, d_W_1 = d_W_1, 
             d_W_2 = d_W_2, d_B_2 = d_B_2, p_3 = p_3, d_W_3 = d_W_3, d_B_3 = d_B_3, 
             d_W_4 = d_W_4, d_B_4 = d_B_4,
             sigmaSqHyperPrior = sigmaSqHyperPrior, ardHyperHyperPrior = ardHyperHyperPrior,
             sparseHyperHyperPrior = sparseHyperHyperPrior, J = J, N = N, SigmaHat = SigmaHat)

#fit <- stan(file = "../../Stan/CcaGenHierarchical.stan", data = data, chains = 4, iter = 2000, refresh = 10)

mHier <- stan_model(file = "../../Stan/CcaGenHierarchicalPi.stan")
system.time(viHier <- vb(mHier, data = data))
#system.time(opHier <- optimizing(mHier, data = data, iter = 10000))
```

# MAP Estimate

```{r}
opHier$par[c("Sigma_theta_W_0")]

map <- opHier$par
theta_W_0_Gsw_med <- map[1:5]
theta_W_1_Gsw_med <- (map[grepl("theta_W_1", names(map))])[1:d_W_1]
theta_W_2_Gsw_med <- (map[grepl("theta_W_2", names(map))])[1:d_W_2]
theta_W_3_Gsw_med <- (map[grepl("theta_W_3", names(map))])[1:d_W_3]
theta_W_4_Gsw_med <- (map[grepl("theta_W_4", names(map))])[1:d_W_4]

lambda_0_med <- c(map["lambda_0[1,1]"],map["lambda_0[1,2]"])
lambda_1_med <- c(map["lambda_1[1,1]"],map["lambda_1[1,2]"])
lambda_2_med <- c(map["lambda_2[1,1]"],map["lambda_2[1,2]"])
lambda_3_med <- c(map["lambda_3[1,1]"],map["lambda_3[1,2]"])
lambda_4_med <- c(map["lambda_4[1,1]"],map["lambda_4[1,2]"])

W_0_Gsw_med <- InverseGivensTransform(theta_W_0_Gsw, n_0, p_common)
dimnames(W_0_Gsw_med) <- list(names(coagTestsStnd)[1:4], c("Latent1", "Latent2"))
W_0_Gsw * lambda_0_med

W_1_Gsw_med <- InverseGivensTransform(theta_W_1_Gsw, n_1, p_common)
dimnames(W_1_Gsw_med) <- list(names(coagTestsStnd)[5:10], c("Latent1", "Latent2"))
W_1_Gsw * lambda_1_med

W_2_Gsw_med <- InverseGivensTransform(theta_W_2_Gsw, n_2, p_common)
dimnames(W_2_Gsw_med) <- list(names(coagTestsStnd)[11:14], c("Latent1", "Latent2"))
W_2_Gsw * lambda_2_med

W_3_Gsw_med <- InverseGivensTransform(theta_W_3_Gsw, n_3, p_common)
dimnames(W_3_Gsw_med) <- list(names(coagTestsStnd)[15:23], c("Latent1", "Latent2"))
W_3_Gsw_med * lambda_3_med

#InverseGivensTransform(theta_W_4_Gsw_med, n_4, p_common)

RightRotateCounterClockwise(diag(2), theta_W_4_Gsw,1,2) * lambda_4_med
```

# Most Representative Sample

```{r}
s <- extract(viHier)
#sampleId <- floor(runif(1,1,1000))
sampleId <- 75

getSamplesCloseToMed(s$theta_W_0[,2,2]) %>%
  intersect(getSamplesCloseToMed(s$theta_W_1[,2,2])) %>%
  intersect(getSamplesCloseToMed(s$theta_W_2[,2,2])) %>%
  intersect(getSamplesCloseToMed(s$theta_W_3[,2,2]))

getSamplesCloseToMed <- function(x) {
  lower <- quantile(x, probs = c(0.4,0.6))[1]
  upper <- quantile(x, probs = c(0.4,0.6))[2]
  
  return(which(x >= lower & x <= upper))
}

theta_W_0_Gsw <- s$theta_W_0[sampleId,1,]
theta_W_1_Gsw <- s$theta_W_1[sampleId,1,]
theta_W_2_Gsw <- s$theta_W_2[sampleId,1,]
theta_W_3_Gsw <- s$theta_W_3[sampleId,1,]
theta_W_4_Gsw <- s$theta_W_4[sampleId,1,]

lambda_0 <- s$lambda_0[sampleId,1,]
lambda_1 <- s$lambda_1[sampleId,1,]
lambda_2 <- s$lambda_2[sampleId,1,]
lambda_3 <- s$lambda_3[sampleId,1,]
lambda_4 <- s$lambda_4[sampleId,1,]

W_0_Gsw <- InverseGivensTransform(theta_W_0_Gsw, n_0, p_common)
dimnames(W_0_Gsw) <- list(names(coagTestsStnd)[1:4], c("Latent1", "Latent2"))
W_0_Gsw * lambda_0

W_1_Gsw <- InverseGivensTransform(theta_W_1_Gsw, n_1, p_common)
dimnames(W_1_Gsw) <- list(names(coagTestsStnd)[5:10], c("Latent1", "Latent2"))
W_1_Gsw * lambda_1

W_2_Gsw <- InverseGivensTransform(theta_W_2_Gsw, n_2, p_common)
dimnames(W_2_Gsw) <- list(names(coagTestsStnd)[11:14], c("Latent1", "Latent2"))
W_2_Gsw * lambda_2

W_3_Gsw <- InverseGivensTransform(theta_W_3_Gsw, n_3, p_common)
dimnames(W_3_Gsw) <- list(names(coagTestsStnd)[15:23], c("Latent1", "Latent2"))
W_3_Gsw * lambda_3

#InverseGivensTransform(theta_W_4_Gsw_med, n_4, p_common)

RightRotateCounterClockwise(diag(2), theta_W_4_Gsw,1,2) * lambda_4
```


# Median Samples

```{r}
posterior <- as.array(viHier)
mcmc_intervals(posterior, pars = c("theta_W_0[1,1]", "theta_W_0[2,1]", "theta_W_0[3,1]", "theta_W_0[4,1]", "theta_W_0[5,1]", "theta_W_0[6,1]", "theta_W_0[7,1]"))
mcmc_intervals(posterior, pars = c("theta_W_4[1,1]", "theta_W_4[2,1]", "theta_W_4[3,1]", "theta_W_4[4,1]", "theta_W_4[5,1]", "theta_W_4[6,1]", "theta_W_4[7,1]"))
mcmc_intervals(posterior, pars = c("theta_W_0[1,2]", "theta_W_0[2,2]", "theta_W_0[3,2]", "theta_W_0[4,2]", "theta_W_0[5,2]", "theta_W_0[6,2]", "theta_W_0[7,2]"))

posteriorMedian <- summary(vi)$summary[,"50%"]
theta_W_0_Gsw_med <- posteriorMedian[1:5]
theta_W_1_Gsw_med <- (posteriorMedian[grepl("theta_W_1", names(posteriorMedian))])[1:d_W_1]
theta_W_2_Gsw_med <- (posteriorMedian[grepl("theta_W_2", names(posteriorMedian))])[1:d_W_2]
theta_W_3_Gsw_med <- (posteriorMedian[grepl("theta_W_3", names(posteriorMedian))])[1:d_W_3]
theta_W_4_Gsw_med <- (posteriorMedian[grepl("theta_W_4", names(posteriorMedian))])[1:d_W_4]

lambda_0_med <- c(posteriorMedian["lambda_0[1,1]"],posteriorMedian["lambda_0[1,2]"])
lambda_1_med <- c(posteriorMedian["lambda_1[1,1]"],posteriorMedian["lambda_1[1,2]"])
lambda_2_med <- c(posteriorMedian["lambda_2[1,1]"],posteriorMedian["lambda_2[1,2]"])
lambda_3_med <- c(posteriorMedian["lambda_3[1,1]"],posteriorMedian["lambda_3[1,2]"])
lambda_4_med <- c(posteriorMedian["lambda_4[1,1]"],posteriorMedian["lambda_4[1,2]"])

W_0_Gsw_med <- InverseGivensTransform(theta_W_0_Gsw, n_0, p_common)
dimnames(W_0_Gsw_med) <- list(names(coagTestsStnd)[1:4], c("Latent1", "Latent2"))
W_0_Gsw * lambda_0_med

W_1_Gsw_med <- InverseGivensTransform(theta_W_1_Gsw, n_1, p_common)
dimnames(W_1_Gsw_med) <- list(names(coagTestsStnd)[5:10], c("Latent1", "Latent2"))
W_1_Gsw * lambda_1_med

W_2_Gsw_med <- InverseGivensTransform(theta_W_2_Gsw, n_2, p_common)
dimnames(W_2_Gsw_med) <- list(names(coagTestsStnd)[11:14], c("Latent1", "Latent2"))
W_2_Gsw * lambda_2_med

W_3_Gsw_med <- InverseGivensTransform(theta_W_3_Gsw, n_3, p_common)
dimnames(W_3_Gsw_med) <- list(names(coagTestsStnd)[15:23], c("Latent1", "Latent2"))
W_3_Gsw_med * lambda_3_med

#InverseGivensTransform(theta_W_4_Gsw_med, n_4, p_common)

RightRotateCounterClockwise(diag(2), theta_W_4_Gsw_med,1,2) * lambda_4_med

mcmc_intervals(posterior, pars = c("lambda_4_reversed[1,1]", "lambda_4_reversed[1,2]"))
#mcmc_intervals(posterior, pars = c("gamma_4_reversed[1,1]", "gamma_4_reversed[1,2]"))
```

Component 1: high bp; low BUN, low basedefexc, low pao2; high wbc, high hematocrit; low D-dimer; high PT
Component 2:

```{r}
theta_W_0_Mvc_med <- posteriorMedian[(2*d_W_0+1):(3*d_W_0)]
theta_W_1_Mvc_med <- (posteriorMedian[grepl("theta_W_1", names(posteriorMedian))])[(2*d_W_1+1):(3*d_W_1)]
theta_W_2_Mvc_med <- (posteriorMedian[grepl("theta_W_2", names(posteriorMedian))])[(2*d_W_2+1):(3*d_W_2)]
theta_W_3_Mvc_med <- (posteriorMedian[grepl("theta_W_3", names(posteriorMedian))])[(2*d_W_3+1):(3*d_W_3)]
theta_W_4_Mvc_med <- (posteriorMedian[grepl("theta_W_4", names(posteriorMedian))])[(2*d_W_4+1):(3*d_W_4)]

InverseGivensTransform(theta_W_0_Mvc_med, n_0, p_common)
InverseGivensTransform(theta_W_1_Mvc_med, n_1, p_common)
InverseGivensTransform(theta_W_2_Mvc_med, n_2, p_common)
InverseGivensTransform(theta_W_3_Mvc_med, n_3, p_common)
InverseGivensTransform(theta_W_4_Mvc_med, n_4, p_common)
```


```{r}
mcmc_intervals(posterior, pars = c("lambda_0_reversed[1,1]", "lambda_0_reversed[2,1]", "lambda_0_reversed[3,1]", "lambda_0_reversed[4,1]", "lambda_0_reversed[5,1]", "lambda_0_reversed[6,1]", "lambda_0_reversed[7,1]"))
mcmc_intervals(posterior, pars = c("lambda_0_reversed[1,2]", "lambda_0_reversed[2,2]", "lambda_0_reversed[3,2]", "lambda_0_reversed[4,2]", "lambda_0_reversed[5,2]", "lambda_0_reversed[6,2]", "lambda_0_reversed[7,2]"))
```

```{r}
mcmc_intervals(posterior, pars = c("theta_W_3[1,1]", "theta_W_3[2,1]", "theta_W_3[3,1]", "theta_W_3[4,1]", "theta_W_3[5,1]", "theta_W_3[6,1]", "theta_W_3[7,1]"))
mcmc_intervals(posterior, pars = c("theta_W_3[1,2]", "theta_W_3[2,2]", "theta_W_3[3,2]", "theta_W_3[4,2]", "theta_W_3[5,2]", "theta_W_3[6,2]", "theta_W_3[7,2]"))
```

